---
title: "Main_Analysis_Study1"
author: "Ourouk Scylla Lucas Gautier"
date: '2023-06-20'
output: html_document
---

This script is the main analysis script for the project "Threat_Spatial Cueing" that study the impact of a threat on attention processes. It use a spatial cueing paradigm and want to replicate the results of Normand et al., (2014) of a reinforcement of the contingent attentional capture using the Threat of Screams paradigm instead of a self-evaluative threat.

The OSf link of this project is available at: https://osf.io/jkt9m/


```{r Knit options, include = FALSE}
knitr::knit_hooks$set(
   error = function(x, options) {
     paste('\n\n<div class="alert alert-danger">',
           gsub('##', '\n', gsub('^##\ Error', '**Error**', x)),
           '</div>', sep = '\n')
   },
   warning = function(x, options) {
     paste('\n\n<div class="alert alert-warning">',
           gsub('##', '\n', gsub('^##\ Warning:', '**Warning**', x)),
           '</div>', sep = '\n')
   },
   message = function(x, options) {
     paste('\n\n<div class="alert alert-info">',
           gsub('##', '\n', x),
           '</div>', sep = '\n')
   }
)
```

# Set Up environments
```{r Package Loading, include = FALSE}

cat("\014") # clear console

# Load packages

# 4 lines : Installs (if necessary) and loads the packages you enter in the 1st row
# 1st row : Creates a list of packages names that you want to use in the script (there is virtually no limit in how much package you can put here)
# 2nd row : Creates a list of packages that have not been installed yet (new packages)
# 3rd row : Installs the new packages
# 4th row : Loads all the listed packages
list.of.packages <- c("dplyr", "emmeans", "tidyverse", "readr", "psych", "lmerTest", "mice", "VIM", "missForest", "lavaan", "semPlot", "lattice")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)
invisible(lapply(list.of.packages, require, character.only = TRUE))

#rm(list=ls()) # clear workspace
rm("list.of.packages", "new.packages")

set.seed(42) # set overall random seed for reproducibility
```

# Aim of the script : 
Run main analysis for the Threat_SpatialCueing project.


# Open the dataframe

```{r Opening file}

df_Total <- read_csv("Data/Transformed_Data/Final_df_Threat_SpatialCueing.csv")

# Transform participant ID in a factor
df_Total$response_id <- factor(df_Total$response_id)

df_Total$RT <- as.numeric(df_Total$RT)


```


# Build secondary dataframes

Here, we build dataframes that only contains Response Time rows, we remove participants who have too many false answers, or bad response times based on our preregistration.

## Survey removing


```{r Survey Removing}

tmp <- df <- df_Total

tmp <- tmp %>%
  filter(Check_Sound == 1)
warning(paste0("We removed participants who said they did not hear any sounds during the experiment. The number of rows we removed is n = ", nrow(df[df$Check_Sound == 2, ]), ". The number of participants after this suppression is N = ", nlevels(factor(tmp$response_id))))


df <- tmp

rm(list=setdiff(ls(), c("df_Total", "df"))) # clear workspace except the dataframes

```



## Remove Sound rows

```{r Sound rows removing}

tmp <- df

tmp <- tmp %>%
  select(-c(Sound_Nb, Sound))

tmp_Locate <- tmp %>%
  filter(Task_Type_str  == "Localization")
df_Locate <- tmp_Locate  


tmp_Catego <- tmp %>%
  filter(Task_Type_str  == "Categorization")
df_Catego <- tmp_Catego


tmp_Locate <- tmp_Locate %>% 
  filter(Task == "Trial")
warning(paste0("We have removed Sound rows in order to keep only Response times trial rows. For participants assigned to the Localization task, the number of rows we removed is n = ", table(df_Locate$Task)[[1]], " which means ",table(df_Locate$Task)[[1]]/nlevels(factor(df_Locate$response_id)) , " lines by participant."))

tmp_Catego <- tmp_Catego %>% 
  filter(Task == "Trial")
warning(paste0("We have removed Sound rows in order to keep only Response times trial rows. For participants assigned to the Categorization task, the number of rows we removed is n = ", table(df_Catego$Task)[[1]], " which means ",table(df_Catego$Task)[[1]]/nlevels(factor(df_Catego$response_id)) , " lines by participant."))

df_Locate <- tmp_Locate  
df_Catego <- tmp_Catego

rm(list=setdiff(ls(), c("df_Total", "df_Locate", "df_Catego"))) # clear workspace except the dataframes

```


```{r Participant Accuracy}

Accuracy_Df <- df_Locate %>%
  group_by(response_id) %>%
  summarise(Accuracy=(length(which(Response_Status == 1))/length(response_id)), n=length(response_id))
View(Accuracy_Df)

hist(Accuracy_Df$Accuracy)

```


## Trial Removing: Incorrect and NoResponse trials

```{r NoResponse}

tmp_Locate <- df_Locate  
tmp_Catego <- df_Catego

## Localization Task
tmp_Locate <- tmp_Locate %>%
  filter(Response_Status == 1)

## Categorization Task
tmp_Catego <- tmp_Catego %>%
  filter(Response_Status == 1)


warning(paste0("We have removed participants trials without any respnse in the response time interval (<1500ms) or with incorrect answers. For participants assigned to the Localization task, the number of rows we removed for incorrect answer is n = ", table(df_Locate$Response_Status)[[2]], ", and the number of rows we removed for incorrect answer is n = ", table(df_Locate$Response_Status)[[3]], ". It means a total of n = ", (table(df_Locate$Response_Status)[[2]]+table(df_Locate$Response_Status)[[3]]), " removed rows."))

warning(paste0("We have removed participants trials without any respnse in the response time interval (<1500ms) or with incorrect answers. For participants assigned to the Localization task, the number of rows we removed for incorrect answer is n = ", table(df_Catego$Response_Status)[[2]], ", and the number of rows we removed for incorrect answer is n = ", table(df_Catego$Response_Status)[[3]], ". It means a total of n = ", (table(df_Catego$Response_Status)[[2]]+table(df_Catego$Response_Status)[[3]]), " removed rows."))

df_Locate <- tmp_Locate  
df_Catego <- tmp_Catego

rm(list=setdiff(ls(), c("df_Total", "df_Locate", "df_Catego"))) # clear workspace except the dataframes

```

### Quintile dataframes
####Localization

```{r Quintile dataframes}

df_Locate$RT <- as.numeric(df_Locate$RT)

# Remove Training trials
tmp <- df_Locate %>%
  filter(Block != "Training") 

# Remove Neutral trials
tmp <- tmp %>%
  filter(Congruency != "NoCongruency")

# recode variables

tmp$Congruency_C <- -0.5*(tmp$Congruency =="Incongruent") + 0.5*(tmp$Congruency =="Congruent")
tmp$Validity_C <- -0.5*(tmp$Cueing_Validity =="Invalid") + 0.5*(tmp$Cueing_Validity =="Valid")
tmp$Condition_C <- +0.5*(tmp$Block =="Threat") + -0.5*(tmp$Block =="Control")

df_Locate <- tmp
warning("This script have been put here but also exist in other chunks....")

df_Locate_Q1 <- df_Locate %>%
  group_by(response_id) %>%
  filter(RT >= quantile(as.numeric(df_Locate$RT), 0) & RT <= quantile(as.numeric(df_Locate$RT), 0.2))

# Group the data by participant and trial types, and calculate the first quintile
df_Locate_Q1bis <- df_Locate %>%
  group_by(response_id, Validity_C, Congruency_C) %>%
  mutate(quintile = ntile(RT, 5)) %>%
  filter(quintile == 1) %>%
  ungroup()

df_Locate_Q2 <- df_Locate %>%
  group_by(response_id) %>%
  filter(RT > quantile(as.numeric(df_Locate$RT), 0.2) & RT <= quantile(as.numeric(df_Locate$RT), 0.4))

# Group the data by participant and trial types, and calculate the first quintile
df_Locate_Q2bis <- df_Locate %>%
  group_by(response_id, Validity_C, Congruency_C) %>%
  mutate(quintile = ntile(RT, 5)) %>%
  filter(quintile == 2) %>%
  ungroup()

df_Locate_Q3 <- df_Locate %>%
  group_by(response_id) %>%
  filter(RT > quantile(as.numeric(df_Locate$RT), 0.4) & RT <= quantile(as.numeric(df_Locate$RT), 0.6))

# Group the data by participant and trial types, and calculate the first quintile
df_Locate_Q3bis <- df_Locate %>%
  group_by(response_id, Validity_C, Congruency_C) %>%
  mutate(quintile = ntile(RT, 5)) %>%
  filter(quintile ==3) %>%
  ungroup()

df_Locate_Q4 <- df_Locate %>%
  group_by(response_id) %>%
  filter(RT > quantile(as.numeric(df_Locate$RT), 0.6) & RT <= quantile(as.numeric(df_Locate$RT), 0.8))

# Group the data by participant and trial types, and calculate the first quintile
df_Locate_Q4bis <- df_Locate %>%
  group_by(response_id, Validity_C, Congruency_C) %>%
  mutate(quintile = ntile(RT, 5)) %>%
  filter(quintile == 4) %>%
  ungroup()

df_Locate_Q5 <- df_Locate %>%
  group_by(response_id) %>%
  filter(RT > quantile(as.numeric(df_Locate$RT), 0.8) & RT <= quantile(as.numeric(df_Locate$RT), 0.97))

# Group the data by participant and trial types, and calculate the first quintile
df_Locate_Q5bis <- df_Locate %>%
  group_by(response_id, Validity_C, Congruency_C) %>%
  mutate(quintile = ntile(RT, 5)) %>%
  filter(quintile == 5) %>%
  ungroup()
warning("There is a problème on this quintile separation with the fifth quintile...")


ifelse(identical(nrow(df_Locate),(nrow(df_Locate_Q1bis)+nrow(df_Locate_Q2bis)+nrow(df_Locate_Q3bis)+nrow(df_Locate_Q4bis)+nrow(df_Locate_Q5bis)))==TRUE, ("The number of participants in the overall dataframe match the number of participants in each quintile dataframe"),("Warning: The number of participants in the overall dataframe do not match the number of participants in each quintile dataframe"))



```

### Quintile dataframes
#### Categorization

```{r Quintile dataframes}

df_Catego$RT <- as.numeric(df_Catego$RT)

# Remove Training trials
tmp <- df_Catego %>%
  filter(Block != "Training") 

# Remove Neutral trials
tmp <- tmp %>%
  filter(Congruency != "NoCongruency")

# recode variables

tmp$Congruency_C <- -0.5*(tmp$Congruency =="Incongruent") + 0.5*(tmp$Congruency =="Congruent")
tmp$Validity_C <- -0.5*(tmp$Cueing_Validity =="Invalid") + 0.5*(tmp$Cueing_Validity =="Valid")
tmp$Condition_C <- +0.5*(tmp$Block =="Threat") + -0.5*(tmp$Block =="Control")

df_Catego <- tmp
warning("This script have been put here but also exist in other chunks....")

df_Catego_Q1 <- df_Catego %>%
  group_by(response_id) %>%
  filter(RT >= quantile(as.numeric(df_Catego$RT), 0) & RT <= quantile(as.numeric(df_Catego$RT), 0.2))

df_Catego_Q2 <- df_Catego %>%
  group_by(response_id) %>%
  filter(RT > quantile(as.numeric(df_Catego$RT), 0.2) & RT <= quantile(as.numeric(df_Catego$RT), 0.4))

df_Catego_Q3 <- df_Catego %>%
  group_by(response_id) %>%
  filter(RT > quantile(as.numeric(df_Catego$RT), 0.4) & RT <= quantile(as.numeric(df_Catego$RT), 0.6))

df_Catego_Q4 <- df_Catego %>%
  group_by(response_id) %>%
  filter(RT > quantile(as.numeric(df_Catego$RT), 0.6) & RT <= quantile(as.numeric(df_Catego$RT), 0.8))

df_Catego_Q5 <- df_Catego %>%
  group_by(response_id) %>%
  filter(RT > quantile(as.numeric(df_Catego$RT), 0.8) & RT <= quantile(as.numeric(df_Catego$RT), 0.97))
warning("There is a problème on this quintile separation with the fifth quintile...")


ifelse(identical(nrow(df_Catego),(nrow(df_Catego_Q1)+nrow(df_Catego_Q2)+nrow(df_Catego_Q3)+nrow(df_Catego_Q4)+nrow(df_Catego_Q5)))==TRUE, ("The number of participants in the overall dataframe match the number of participants in each quintile dataframe"),("Warning: The number of participants in the overall dataframe do not match the number of participants in each quintile dataframe"))



```


## Mad removing

```{r Mad removing}

tmp_Locate <- df_Locate  
tmp_Catego <- df_Catego

## Localization Task

Median_Locate <- median(as.numeric(tmp_Locate$RT))
Mad_tmp_Locate <- mad(as.numeric(tmp_Locate$RT))
Mad_Before_Locate <- nrow(tmp_Locate)

tmp_Locate <- tmp_Locate %>%
  mutate(RT = as.numeric(RT)) %>%
  filter((RT >= median(RT)-3*mad(RT)) & (RT <= median(RT)+3*mad(RT)))

Mad_After_Locate <- nrow(tmp_Locate)
Mad_Exclusion_Locate <- Mad_Before_Locate - Mad_After_Locate


## Categorization Task

Median_Catego <- median(as.numeric(tmp_Catego$RT))
Mad_tmp_Catego <- mad(as.numeric(tmp_Catego$RT))
Mad_Before_Catego <- nrow(tmp_Catego)

tmp_Catego <- tmp_Catego %>%
  mutate(RT = as.numeric(RT)) %>%
  filter((RT >= median(RT)-3*mad(RT)) & (RT <= median(RT)+3*mad(RT)))

Mad_After_Catego <- nrow(tmp_Catego)
Mad_Exclusion_Catego <- Mad_Before_Catego - Mad_After_Catego



warning(paste0("We have removed participants response time < or > to 3 mad. For participants assigned to the Localization task, the number of rows we removed is n = ", Mad_Exclusion_Locate, " whith means 3 times  ", Mad_tmp_Locate , " around the median: ", Median_Locate))

warning(paste0("We have removed participants response time < or > to 3 mad. For participants assigned to the Categorization task, the number of rows we removed is n = ", Mad_Exclusion_Catego, " whith means 3 times  ", Mad_tmp_Catego , " around the median: ", Median_Catego))


#sum(((df$RT >= median(df$RT)-3*mad(df$RT)) & (df$RT <= median(df$RT)+3*mad(df$RT)))==FALSE)

df_Locate_Mad <- tmp_Locate
df_Catego_Mad <- tmp_Catego

rm(list=setdiff(ls(), c("df_Total", "df_Locate", "df_Catego", "df_Locate_Mad", "df_Catego_Mad"))) # clear workspace except the dataframes


```


# Main analysis

## Localization task

### Means

```{r Means Localiation}

df_Locate <- df_Locate %>%
  filter(Block != "Training") 

df_Locate_Mad <- df_Locate_Mad %>%
  filter(Block != "Training") 

# Mean by condition
Mean1 <- df_Locate_Mad %>% 
  group_by(Block) %>%
  summarise(mean=mean(RT), sd=sd(RT), se=(sd(RT)/sqrt(length(response_id))), n=length(response_id))
view(Mean1)

# Graphic representation
ggplot(Mean1, aes(x = Block, y = mean)) +
  geom_point() +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = 0.1) +
  geom_line() +
  xlab("Condition") +
  ylab("Response time")

# Mean by condition*Congruency*Validity
Mean2 <- df_Locate %>% 
  group_by(Block, Congruency, Cueing_Validity) %>%
  summarise(mean=mean(RT), sd=sd(RT), se=(sd(RT)/sqrt(length(response_id))),  n=length(response_id))
view(Mean2)

# If we run the same analysis but after removing rows >3Mad
Mean2Mad <- df_Locate_Mad %>% 
  group_by(Block, Congruency, Cueing_Validity) %>%
  summarise(mean=mean(RT), sd=sd(RT), se=(sd(RT)/sqrt(length(response_id))),  n=length(response_id))
view(Mean2Mad)

# Graphic representation
ggplot(Mean2, aes(x = Block, y = mean, color = Cueing_Validity, linetype = Congruency, group = interaction(Cueing_Validity, Congruency))) +
  geom_point(position = position_dodge(width = 0.2)) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = 0.1, position = position_dodge(width = 0.2)) +
  geom_line(,position = position_dodge(width = 0.2)) +
  xlab("Condition") +
  ylab("Response time") +
  scale_color_manual(values = c("red", "black", "green4"), guide = guide_legend(title = "Cueing_Validity")) +
  scale_linetype_manual(values = c("solid", "52", "22"), guide = guide_legend(title = "Congruency"))

# If we run the same analysis but after removing rows >3Mad
ggplot(Mean2Mad, aes(x = Block, y = mean, color = Cueing_Validity, linetype = Congruency, group = interaction(Cueing_Validity, Congruency))) +
  geom_point(position = position_dodge(width = 0.2)) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = 0.1, position = position_dodge(width = 0.2)) +
  geom_line(,position = position_dodge(width = 0.2)) +
  xlab("Condition") +
  ylab("Response time") +
    scale_color_manual(values = c("red", "black", "green4"), guide = guide_legend(title = "Cueing_Validity")) +
  scale_linetype_manual(values = c("solid", "52", "22"), guide = guide_legend(title = "Congruency"))



# tmp_NoCue <- df_Locate %>%
#   filter(Block != "Training") %>%
#   filter(Congruency == "NoCongruency")
# tmp_NoCue$Condition_C <- +0.5*(tmp_NoCue$Block =="Threat") -0.5*(tmp_NoCue$Block =="Toon") + -0.5*(tmp_NoCue$Block =="Control")
# 
# lmer0 <- lmer(RT ~ Condition_C 
#               + (Condition_C| response_id),
#               data = tmp_NoCue)
# 
# summary(lmer0)

Ppt_Nb_row <- df_Locate_Q1 %>% 
  group_by(response_id, Block, Congruency, Cueing_Validity) %>%
  summarise(mean=mean(RT), sd=sd(RT), n=length(response_id))

```



### 3 way interaction
#### Localization

```{r Localization: 3 way interaction}
nlevels(factor(df_Locate$response_id))

# Define linear mixed model

lmer1 <- lmer(RT ~ Congruency_C * Validity_C * Condition_C 
              + (Congruency_C*Validity_C*Condition_C| response_id),
              data = df_Locate)

summary(lmer1)

tmp_Locate_Residuals <- df_Locate %>%
  filter(Congruency != "NoCongruency") %>%
  mutate(Hat = hatvalues(lmer1)) %>%
  mutate(Rstud = rstudent(lmer1))%>%
  mutate(Cook = cooks.distance(lmer1))

tmp_Locate_Residuals_Rm <- tmp_Locate_Residuals %>%
  filter(Rstud <= 3 & Rstud >= -3) %>%
  filter(Hat <= .10) %>%
  filter(Cook <= .10)

tmp_Locate_Residuals_Rm$Congruency_C <- -0.5*(tmp_Locate_Residuals_Rm$Congruency =="Incongruent") + 0.5*(tmp_Locate_Residuals_Rm$Congruency =="Congruent")
tmp_Locate_Residuals_Rm$Validity_C <- -0.5*(tmp_Locate_Residuals_Rm$Cueing_Validity =="Invalid") + 0.5*(tmp_Locate_Residuals_Rm$Cueing_Validity =="Valid")
tmp_Locate_Residuals_Rm$Condition_C <- +0.5*(tmp_Locate_Residuals_Rm$Block =="Threat") + -0.5*(tmp_Locate_Residuals_Rm$Block =="Control")

lmer1_WResid <- lmer(RT ~ Congruency_C * Validity_C * Condition_C 
              + (Congruency_C*Validity_C*Condition_C| response_id),
              data = tmp_Locate_Residuals_Rm)

summary(lmer1_WResid)


### With the Mad dataframe

tmp_Locate_Mad <- df_Locate_Mad %>%
  filter(Congruency != "NoCongruency")

tmp_Locate_Mad$Congruency_C <- -0.5*(tmp_Locate_Mad$Congruency =="Incongruent") + 0.5*(tmp_Locate_Mad$Congruency =="Congruent")
tmp_Locate_Mad$Validity_C <- -0.5*(tmp_Locate_Mad$Cueing_Validity =="Invalid") + 0.5*(tmp_Locate_Mad$Cueing_Validity =="Valid")
tmp_Locate_Mad$Condition_C <- +0.5*(tmp_Locate_Mad$Block =="Threat") + -0.5*(tmp_Locate_Mad$Block =="Control")

lmer1_Mad <- lmer(RT ~ Congruency_C * Validity_C * Condition_C 
              + (Congruency_C*Validity_C*Condition_C| response_id),
              data = tmp_Locate_Mad)

summary(lmer1_Mad)

tmp_Locate_Mad_Residuals <- df_Locate_Mad %>%
  filter(Congruency != "NoCongruency") %>%
  mutate(Hat = hatvalues(lmer1_Mad)) %>%
  mutate(Rstud = rstudent(lmer1_Mad))%>%
  mutate(Cook = cooks.distance(lmer1_Mad))

tmp_Locate_Mad_Residuals_Rm <- tmp_Locate_Mad_Residuals %>%
  filter(Rstud <= 3 & Rstud >= -3) %>%
  filter(Hat <= .10) %>%
  filter(Cook <= .10)

tmp_Locate_Mad_Residuals_Rm$Congruency_C <- -0.5*(tmp_Locate_Mad_Residuals_Rm$Congruency =="Incongruent") + 0.5*(tmp_Locate_Mad_Residuals_Rm$Congruency =="Congruent")
tmp_Locate_Mad_Residuals_Rm$Validity_C <- -0.5*(tmp_Locate_Mad_Residuals_Rm$Cueing_Validity =="Invalid") + 0.5*(tmp_Locate_Mad_Residuals_Rm$Cueing_Validity =="Valid")
tmp_Locate_Mad_Residuals_Rm$Condition_C <- +0.5*(tmp_Locate_Mad_Residuals_Rm$Block =="Threat") + -0.5*(tmp_Locate_Mad_Residuals_Rm$Block =="Control")

lmer1_Mad_WResid <- lmer(RT ~ Congruency_C * Validity_C * Condition_C 
              + (Congruency_C*Validity_C*Condition_C| response_id),
              data = tmp_Locate_Mad_Residuals_Rm)

summary(lmer1_Mad_WResid)


## Removing Toon trials
tmp_Locate_Mad_Residuals_Rm_NoToon <- tmp_Locate_Mad_Residuals_Rm %>%
    filter(Block != "Toon")


lmer1_Mad_WResid_NoToon <- lmer(RT ~ Congruency_C * Validity_C * Condition_C 
              + (Congruency_C*Validity_C*Condition_C| response_id),
              data = tmp_Locate_Mad_Residuals_Rm_NoToon)

summary(lmer1_Mad_WResid_NoToon)

## Removing Control trials
tmp_Locate_Mad_Residuals_Rm_NoCtrl <- tmp_Locate_Mad_Residuals_Rm %>%
    filter(Block != "Control")


lmer1_Mad_WResid_NoCtrl <- lmer(RT ~ Congruency_C * Validity_C * Condition_C 
              + (Congruency_C*Validity_C*Condition_C| response_id),
              data = tmp_Locate_Mad_Residuals_Rm_NoCtrl)

summary(lmer1_Mad_WResid_NoCtrl)


# df_Recod$Levier_Anova_ControlInduction<-hatvalues(Anova_ControlInduction) # Calculate the hat values for each ppt
# df_Recod$ResidStudent_Anova_ControlInduction<-rstudent(Anova_ControlInduction) # Calculate the student residuals for each ppt : it could reaveal a problem beacause some score are higher than 3
# df_Recod$Cook_Anova_ControlInduction<-cooks.distance(Anova_ControlInduction) # Calculate the Cooks distance for each ppt

ranef(lmer1)
coef(lmer1)

xyplot(RT~Fear_Score| response_id, data=tmp, ylab="Response Time", type=c("p","r","g"),layout = c(3,3,31))

qqmath(~RT|response_id,data=tmp,layout = c(3,3,4))
qqmath(~RT|Target_Type,data=tmp,layout = c(2,1,1))

qqnorm(residuals(lmer1))
dotplot(ranef(lmer1))

qqmath(ranef(lmer1))
plot(lmer1) # ou plot(fitted(fitA.lmer),residuals(fitA.lmer))



```

### Main hypothesis by quintile
#### Localization

```{r Localization: 3 way interaction by quintile}


lmer1_Q1 <- lmer(RT ~ Congruency_C * Validity_C * Condition_C 
              + (Congruency_C*Validity_C*Condition_C| response_id),
              data = df_Locate_Q1)

summary(lmer1_Q1)


lmer1_Q2 <- lmer(RT ~ Congruency_C * Validity_C * Condition_C 
              + (Congruency_C*Validity_C*Condition_C| response_id),
              data = df_Locate_Q2)

summary(lmer1_Q2)

lmer1_Q3 <- lmer(RT ~ Congruency_C * Validity_C * Condition_C 
              + (Congruency_C*Validity_C*Condition_C| response_id),
              data = df_Locate_Q3)

summary(lmer1_Q3)

lmer1_Q4 <- lmer(RT ~ Congruency_C * Validity_C * Condition_C 
              + (Congruency_C*Validity_C*Condition_C| response_id),
              data = df_Locate_Q4)

summary(lmer1_Q4)

lmer1_Q5 <- lmer(RT ~ Congruency_C * Validity_C * Condition_C 
              + (Congruency_C*Validity_C*Condition_C| response_id),
              data = df_Locate_Q5)

summary(lmer1_Q5)


lmer1_Q1bis <- lmer(RT ~ Congruency_C * Validity_C * Condition_C 
              + (Congruency_C*Validity_C*Condition_C| response_id),
              data = df_Locate_Q1bis)

summary(lmer1_Q1bis)

lmer1_Q2bis <- lmer(RT ~ Congruency_C * Validity_C * Condition_C 
              + (Congruency_C*Validity_C*Condition_C| response_id),
              data = df_Locate_Q2bis)

summary(lmer1_Q2bis)

lmer1_Q3bis <- lmer(RT ~ Congruency_C * Validity_C * Condition_C 
              + (Congruency_C*Validity_C*Condition_C| response_id),
              data = df_Locate_Q3bis)

summary(lmer1_Q3bis)

lmer1_Q4bis <- lmer(RT ~ Congruency_C * Validity_C * Condition_C 
              + (Congruency_C*Validity_C*Condition_C| response_id),
              data = df_Locate_Q4bis)

summary(lmer1_Q4bis)

lmer1_Q5bis <- lmer(RT ~ Congruency_C * Validity_C * Condition_C 
              + (Congruency_C*Validity_C*Condition_C| response_id),
              data = df_Locate_Q5bis)

summary(lmer1_Q5bis)

```



### 3 way interaction
#### Categorization

```{r Categorization: 3 way interaction}

# Remove Training trials
tmp2 <- df_Catego %>%
  filter(Block != "Training") 

# Remove Neutral trials
tmp2 <- tmp2 %>%
  filter(Congruency != "NoCongruency")

# recode variables

tmp2$Congruency_C <- -0.5*(tmp2$Congruency =="Incongruent") + 0.5*(tmp2$Congruency =="Congruent")
tmp2$Validity_C <- -0.5*(tmp2$Cueing_Validity =="Invalid") + 0.5*(tmp2$Cueing_Validity =="Valid")
tmp2$Condition_C <- +0.5*(tmp2$Block =="Threat") + -0.5*(tmp2$Block =="Control")

# Define linear mixed model

lmer2 <- lmer(RT ~ Congruency_C * Validity_C * Condition_C 
              + (Congruency_C*Validity_C*Condition_C| response_id),
              data = tmp2)

summary(lmer2)




```


```{r Categorization: 3 way interaction by quintile}


lmer2_Q1 <- lmer(RT ~ Congruency_C * Validity_C * Condition_C 
              + (Congruency_C*Validity_C*Condition_C| response_id),
              data = df_Catego_Q1)

summary(lmer2_Q1)

lmer2_Q2 <- lmer(RT ~ Congruency_C * Validity_C * Condition_C 
              + (Congruency_C*Validity_C*Condition_C| response_id),
              data = df_Catego_Q2)

summary(lmer2_Q2)

lmer2_Q3 <- lmer(RT ~ Congruency_C * Validity_C * Condition_C 
              + (Congruency_C*Validity_C*Condition_C| response_id),
              data = df_Catego_Q3)

summary(lmer2_Q3)

lmer2_Q4 <- lmer(RT ~ Congruency_C * Validity_C * Condition_C 
              + (Congruency_C*Validity_C*Condition_C| response_id),
              data = df_Catego_Q4)

summary(lmer2_Q4)

lmer2_Q5 <- lmer(RT ~ Congruency_C * Validity_C * Condition_C 
              + (Congruency_C*Validity_C*Condition_C| response_id),
              data = df_Catego_Q5)

summary(lmer2_Q5)

```

### EFfect of anxiety level on the contingent capture

#### Localization task

```{r EFfect of anxiety level on the contingent }
# Remove Training trials
tmp <- df_Locate %>%
  filter(Block != "Training") 

# Remove Neutral trials
tmp <- tmp %>%
  filter(Congruency != "NoCongruency")

# recode variables

tmp$Congruency_C <- -0.5*(tmp$Congruency =="Incongruent") + 0.5*(tmp$Congruency =="Congruent")
tmp$Validity_C <- -0.5*(tmp$Cueing_Validity =="Invalid") + 0.5*(tmp$Cueing_Validity =="Valid")
tmp$Condition_C <- +0.5*(tmp$Block =="Threat") + -0.5*(tmp$Block =="Control")

# Define linear mixed model

lmer3 <- lmer(RT ~ Congruency_C * Validity_C * Fear_Score 
              + (Congruency_C*Validity_C*Fear_Score| response_id),
              data = tmp)

summary(lmer3)
ranef(lmer3)


tmp_NoToon <- tmp %>%
  filter(Block != "Toon")

# Effect of condition on Fear_Score
lmer3bis <- lmer(Fear_Score ~ Condition_C 
              + (Condition_C| response_id),
              data = tmp)

summary(lmer3bis)
ranef(lmer3bis)


lm3 <- lm(RT ~ Congruency_C * Validity_C * Fear_Score,
              data = tmp)

summary(lm3)

lm3_NoToon <- lm(RT ~ Congruency_C * Validity_C * Fear_Score,
              data = tmp_NoToon)

summary(lm3_NoToon)




```

```{r}
tmp_Full <- rbind(df_Locate, df_Catego)
nlevels(factor(tmp_Full$response_id))


lmer4 <- lmer(RT ~ Counting_Trial * Task_Type_str 
              + (Counting_Trial * Task_Type_str|response_id), data = tmp_Full)

summary(lmer4)

```


```{r}
tmp_Full <- rbind(df_Locate, df_Catego)
nlevels(factor(tmp_Full$response_id))

tmp_Full$Condition_C <- +0.5*(tmp_Full$Block =="Threat") + -0.5*(tmp_Full$Block =="Control")


lmer5 <- lmer(as.numeric(RT) ~ Condition_C * Task_Type_str 
              + (Condition_C * Task_Type_str|response_id), data = tmp_Full)

summary(lmer5)
```


```{r}

tmp_Mad <- df_Locate_Mad %>%
  filter(Block != "Training")

lmer6 <- lmer(RT ~ Fear_Score 
              + (Fear_Score| response_id),
              data = tmp_Mad)

summary(lmer6)
# Ajouter (Counting_Trial) au modèle rend signif l'effet de la peur... 

tmp_Mad_Threat <- df_Locate_Mad %>%
  filter(Block == "Threat")

lmer6_Threat <- lmer(RT ~ Fear_Score 
              + (Fear_Score| response_id),
              data = tmp_Mad_Threat)

summary(lmer6_Threat)
```


```{r Examples}

df_Locate$response_id <- factor(df_Locate$response_id)

xtabs(~response_id+Congruency,df_Locate)

lmer()
summary()
ranef()
coef()


qqmath(~y|pp,data=DF,layout = c(3,3,4))
qqmath(~y|stim,data=DF,layout = c(3,3,4))

qqnorm(residuals(fitA.lmer))
qqmath(ranef(fitA.lmer))
plot(fitA.lmer) # ou plot(fitted(fitA.lmer),residuals(fitA.lmer))




xyplot(RT~Congruency|response_id, data=df_Locate, ylab="Response Time", type=c("p","r","g"),layout = c(3,3,4))
xylowess.fnc(y ~ Condc | pp, data = DF, ylab = "Jugement",layout = c(3,3,4))
dotplot(ranef(fitA.lmer, condVar = TRUE))
# package lattice et langageR

#Pour comparer des modèles :
anova(fitA.lmer,fitC.lmer)

# Pour savoir si surspécifié:
summary(rePCA(m0))

VarCorr(m1) # => extrait seulement les variances de “summary”



```

# Effets du PTSD sur l'anxieté à la suite des condition expérimentale

```{r PTSD on Anxiety}

warning("Ici j'ai fait mes regression avec Fear_Score mais ça donne des trucs un peu differents sur la régression avec PTSD par rapport à si j'utilise Fear_Mean. Le problème vient peut-être du fait que j'ai fait une erreur dans le calcul du Fear_Mean_Pretest que je dois corriger avant de continuer tout ça...")

Short_df <- df %>%
  filter(Block == "Control" | Block == "Threat" | Block == "Toon") %>%
  group_by(response_id, Block) %>%
  slice(1) %>%
  ungroup()

# Build a difference score between pretest and anxiety after each block
Short_df$AnxietyDiff <- Short_df$Fear_Score - Short_df$Fear_Score_Pretest
Short_df$PTSD_Diag_ct <- -0.5*(Short_df$PTSD_Diag =="NoDiag") + 0.5*(Short_df$PTSD_Diag =="Diag")


# Link between PTSD and Anxiety at the beginning of experiment
cor.test(Short_df$PTSD_Score, Short_df$Fear_Score_Pretest) 
summary(lm(Fear_Score_Pretest~PTSD_Score, data = Short_df))
summary(lm(Fear_Score_Pretest~PTSD_Diag, data = Short_df))

# Predict the effect of experimental manipulation (Threat) on anxiety with PTSD_Diag
AnxietyThreat <- Short_df %>%
  filter(Block == "Threat")
summary(lm(AnxietyDiff~PTSD_Diag_ct, data = AnxietyThreat))
# Ca veut dire que le fait d'avoir été diagnostiqué PTSD engendre un moins grand effet des cris sur l'anxiété ressentie

ggplot(AnxietyThreat, aes(x = Fear_Score_Pretest, y = Fear_Score, color = PTSD_Diag)) +
  geom_point() +
  geom_smooth(method = "lm", se = TRUE) +
  xlab("Fear_Score_Pretest") +
  ylab("Fear_Score") +
  labs(color = "PTSD_Diag")

# Predict the effect of experimental manipulation (Threat) on anxiety for non-diagnosed pptEs
AnxietyThreat <- Short_df %>%
  filter(Block == "Threat") %>%
  filter(PTSD_Diag =="NoDiag")
summary(lm(AnxietyDiff~1, data = AnxietyThreat))

# Predict the effect of experimental manipulation (Threat) on anxiety for diagnosed pptEs
AnxietyThreat <- Short_df %>%
  filter(Block == "Threat") %>%
  filter(PTSD_Diag =="Diag")
summary(lm(AnxietyDiff~1, data = AnxietyThreat)) # This result is so WEIRD !!!



```



### Supplementary

##### ANalyse de la latéralité

```{r Laterality}

df_Locate <- df_Locate %>% mutate(Laterality = case_when(Target_Position == "top" ~ "Vertical",
                                                         Target_Position == "bottom" ~ "Vertical",
                                                         Target_Position == "right" ~ "Horizontal",
                                                         Target_Position == "left" ~ "Horizontal",)) %>%
  mutate(Laterality_Cod = case_when(Laterality == "Vertical" ~ -0.5, 
                                    Laterality == "Horizontal" ~ +0.5))

df_Locate$RT <- as.numeric(df_Locate$RT)

df_Catego <- df_Catego %>% mutate(Laterality = case_when(Target_Position == "top" ~ "Vertical",
                                                         Target_Position == "bottom" ~ "Vertical",
                                                         Target_Position == "right" ~ "Horizontal",
                                                         Target_Position == "left" ~ "Horizontal",))%>%
  mutate(Laterality_Cod = case_when(Laterality == "Vertical" ~ -0.5, 
                                    Laterality == "Horizontal" ~ +0.5))

df_Catego$RT <- as.numeric(df_Catego$RT)


lmer_Laterality_Locate <- lmer(RT ~ Laterality_Cod 
              + (Laterality_Cod | response_id),
              data = df_Locate)
summary(lmer_Laterality_Locate)
# Les gens répondent plus rapidement sur les touches horizontales que verticales en tâche de localization

lmer_Laterality_Catego <- lmer(RT ~ Laterality_Cod 
              + (Laterality_Cod | response_id),
              data = df_Catego)
summary(lmer_Laterality_Catego)
# Les gens répondent plus rapidement sur les touches horizontales que verticales en tâche de categorisation


```







